---
title: "Lecture 6 Assignment"
author: "James"
date: "2/1/2023"
output:
  word_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---
(a)
T = 4/(4+17) = 0.19, 19% probability that the two tests agree on the outcome.

(b)
A 'positive' diagnosis is correct(success), so we want to compare pi.1+ = P(Automated = Positive) against pi.+1 = P(Manual = Positive).

(c)
```{r}
alpha <- 0.05
n.11 <- 27; n.10 <- 4
n.01 <- 17; n.00 <- 702
n <- n.11 + n.01 + n.10 + n.00

library(PropCIs)
scoreci.mp(b=n.01, c=n.10, n=n, conf.level = 0.95)
```

(d)
```{r}
n.table <- matrix(data=c(n.11, n.10, n.01, n.00), nrow=2, byrow=TRUE)
mcnemar.test(x=n.table, correct=FALSE)
```

(e)
CI: We are 95% confident that the interval from -0.031 to -0.006 covers the true difference in probability of testing method between Automated and Manual.
Hypothesis test: X^2 = 8.05, p-value = 0.0046, we can reject the null hypothesis with p-value less than 0.05. 
We can conclude that there is a difference in testing methods. with the confidence interval, we can see the the intervals do not contain 0. Therefore we can rule out the possibility that there is no difference in testing methods. From the hypothesis test, we have sufficient evidence to conclude that there is a difference in the probability of testing methods.
